In this section i felt the need to provide a Special words of gratitude to the many persons who have assisted me along the process toward bringing this thesis to completion.

I would like to express my most sincere and great respect to my advisor, Tiago Guimaraes, for his inspiring guidance, valuable insights and endless patience. His technical contributions and encouragement were of extreme relevance in shaping this work, and I am deeply indebted as regards his investment of time and effort in my growth as a researcher.

Also, i would like to mention deeply indebted to Centro Algoritmi for affording me the means and facilities necessary for my work. I would like to thank [Funding Organization] for the financial support that made this work possible.

 On a personal note, I would like to thank as well my family and friends for their unwavering support and encouragement throughout this long and often difficult journey. The hard work with which my parents, Pedro Silva and Helena Silva, passed to me always made me feel like it always pays off in the end, so thanks. Also, the same applies To my close friends within the University context, Tiago Martins and Jonas Barbosa, which made my life at the university easier, bringing motivation, which was an invaluable asset at the most difficult moments.

I would, lastly, extend my appreciation to all those who have, one way or another, contributed toward the completion of this thesis. Without such help, it could not have been completed by me. I shall always be grateful for that fact and i hope this is another set of firm steps to what could be a successful career.

\newpage