This thesis investigates the benefits of adopting private blockchain technologies,
among other recent innovations, within the health sector. Even though organizations
have been concerned about security for a long time, there is a trade-off between security
and the exchange of data between entities across the network. The primary attribute of blockchain
is thus ensured to provide better integrity, security and flexibility in sharing information securely
across a group or consortium of organizations.

During this project two main use cases where created: integration of
Hyperledger Fabric with IPFS  and optimization of management of blockchain
infrastructure by means of contemporary technologies. In further sections, each of these use cases
are deeply elaborated to give an extended look at their practical usage and results.

The first use case would assume the benefits of using Hyperledger Fabric
in combination with IPFS for secure file storage, where a private network of IPFS
would store the files and record hashes on the blockchain for integrity. In the second use case on the other hand,
there is the design and benchmarking of several network infrastructures of blockchain seeking an optimal
configuration. Besides that, there is a discussion about the development of an UI tool for monitoring and analysis
of the status of the network. To this precise use case,more work is expected in the future to enhance this use
case further, to refine even more its robustness, operability and maintainability.

This work will demonstrate such use cases and illustrate how blockchain can enhance data security
and operational efficiency in healthcare while resolving challenges in large-scale implementations.

% Example keywords section with indentation
\vspace{1cm} % Add space before the keywords section
\textbf{Keywords:} \parbox[t]{0.6\textwidth}{\raggedright Blockchain Technology, Blockchain in Healthcare, Healthcare Systems, Hyperledger Fabric, Kubernetes;}
\medskip

\pagebreak
